\documentclass[11pt]{article}
\input{famhack-legal-shared.tex}

\begin{document}

\FHCover
  {Code Of Conduct}
  {Behaviour standards for FamHack participants, organisers, mentors, guests, and anyone interacting with the event online or in person.}
  {FH-CODE-OF-CONDUCT / A4 PORTRAIT / VERSION 2026-03-10}
  {Effective date: 10 March 2026.\newline
  This version applies to the FamHack website, official online channels, and the in-person event environment.}

{\fhbold\fontsize{18}{18}\selectfont FamHack Code of Conduct\par}
\vspace{0.3em}
FamHack is a collaborative event for first-year students, academic parents, and organisers. People should be able to learn, build, compete, and socialise without harassment, pressure, intimidation, or technical sabotage.

\FHCallout{Reporting And Safety}{
Email reports should be sent to famhack2026@gmail.com. If you are on site and need help urgently, speak to any FamHack organiser or the event lead at the registration desk. In an emergency, contact venue staff immediately and call 999.%
}

\vspace{0.6em}
\FHMetaTable{
Applies to & Participants, organisers, volunteers, mentors, speakers, guests, and online community members \\ \hline
Scope & Registration flow, website use, dashboard use, CTF participation, in-person event spaces, and official online channels \\ \hline
Primary reporting route & famhack2026@gmail.com \\ \hline
Urgent in-person contact & Any FamHack organiser on site or the event lead at the registration desk \\ \hline
}

\FHSection{1. Expected Behaviour}
Everyone taking part in FamHack is expected to:
\begin{itemize}
  \item treat other people with respect, patience, and basic professionalism;
  \item make space for newer participants, especially first-year students who may be attending their first event of this kind;
  \item communicate clearly and accept boundaries the first time they are set;
  \item collaborate honestly and give credit fairly;
  \item follow venue rules, organiser instructions, and CTF rules;
  \item stop behaviour immediately if asked by an organiser; and
  \item help keep shared spaces welcoming, accessible, and safe.
\end{itemize}

\newpage
\FHSection{2. Unacceptable Behaviour}
The following behaviour is not acceptable at FamHack:
\begin{itemize}
  \item harassment, discrimination, or hostility based on race, ethnicity, nationality, sex, gender identity, sexuality, disability, religion, age, or similar protected characteristics;
  \item bullying, intimidation, stalking, threats, or sustained disruption;
  \item unwanted sexual attention, sexualised comments, or invasive behaviour;
  \item doxxing, outing, impersonation, or sharing private information without permission;
  \item recording, photographing, or publishing someone in a way that ignores a clear refusal or reasonable privacy expectation;
  \item repeated pressure after someone has said no, disengaged, or asked for distance;
  \item aggressive intoxication, property damage, or unsafe physical conduct; and
  \item cheating, sabotage, denial-of-service activity, account abuse, or attempts to compromise event infrastructure or another participant's work.
\end{itemize}

\FHSection{3. Academic Family Context}
FamHack uses ``parent'' and ``child'' as academic-family role labels only. Those labels do not create permission to control, pressure, isolate, or overstep another person's boundaries.

Participants in more senior positions should be especially careful with power dynamics. A first-year student should never be made to feel that support, inclusion, technical help, or social access depends on tolerating inappropriate behaviour.

\FHSection{4. Technical Conduct And Fair Play}
Because FamHack includes a CTF and technical challenges, the following extra rules apply:
\begin{itemize}
  \item solve the challenges that are intentionally part of the event, not the live infrastructure behind participant accounts or registration;
  \item do not attack rate limits, authentication systems, databases, hosting, or mail delivery;
  \item do not access, modify, or attempt to expose another user's data, credentials, or progress;
  \item do not interfere with another team's demo, code, hardware, or presentation materials; and
  \item if you find a real vulnerability in the event platform, stop and report it privately to organisers instead of exploiting it.
\end{itemize}

\FHSection{5. Reporting A Problem}
If you experience or witness behaviour that may violate this Code of Conduct:
\begin{itemize}
  \item contact an organiser through famhack2026@gmail.com;
  \item if you are on site, speak to any FamHack organiser or the event lead at the registration desk;
  \item if the issue involves immediate danger, contact venue staff immediately and call 999; and
  \item if helpful, write down what happened, who was involved, where it happened, and whether there were witnesses.
\end{itemize}

The organisers should provide at least one reporting route that does not require the reporter to approach the person involved directly.

\FHSection{6. How Reports Will Be Handled}
Organisers should respond promptly, take reports seriously, and share information only with people who need it to respond appropriately.

Depending on the situation, organisers may:
\begin{itemize}
  \item have a private conversation and issue a warning;
  \item require behaviour to stop immediately;
  \item separate participants or restrict contact;
  \item remove someone from a session, challenge, or communication channel;
  \item revoke event participation without refund or prize eligibility, if applicable; and
  \item escalate to venue staff, university processes, or law enforcement where necessary.
\end{itemize}

\FHSection{7. Confidentiality And Limits}
FamHack should treat reports as sensitively as possible, but complete secrecy cannot be guaranteed where someone is at risk, where evidence needs to be checked, or where legal or institutional escalation is required.

The organisers should avoid retaliating against reporters and should not require informal confrontation as a condition of support.

\FHSection{8. Accessibility, Welfare, And Breaks}
Events run better when participants can step back safely. If you need a quieter space, time away from a team area, or help handling an uncomfortable situation, speak to an organiser and we will help arrange appropriate support on the day, including finding a quieter area where possible.

\FHCallout{Welfare Support}{
Participants can ask any organiser for help stepping away from a situation, finding a quieter place, or getting practical support during the event.%
}

\FHSection{9. Consequences For Violations}
Anyone asked to stop unacceptable behaviour is expected to stop immediately. Failure to do so can lead to removal from the event or related platforms.

Serious incidents may justify immediate action without a prior warning. Organisers may also remove content, invalidate submissions, or restrict access to infrastructure where that is necessary to protect participants or the event.

\newpage
\FHSection{10. Contact}
Use the contact points below if you need to report a concern or ask how a report will be handled.

\FHMetaTable{
Reporting channel & famhack2026@gmail.com \\ \hline
On-site lead & Any FamHack organiser on site or the event lead at the registration desk \\ \hline
Emergency procedure & Contact venue staff immediately and call 999 if urgent help is needed \\ \hline
Organising body & FamHack Organising Team, University of Edinburgh \\ \hline
}

\end{document}
